Spatio-angular fluorescence microscopy I. Basic theory (Draft: \today)

### 2018-12-04 papers/basic-theory/paper/paper.tex
Misc edits.

\author{Talon Chandler,\authormark{1,*}, Rudolf Oldenbourg,\authormark{2} and\\ Patrick La Rivi\`ere\authormark{1,2}}

\address{\authormark{1}University of Chicago, Department of Radiology, Chicago, Illinois 60637, USA\\
  \authormark{2}Marine Biological Laboratory, Bell Center, Woods Hole, Massachusetts 02543, USA
}

@@

\subsection{Paraxial dipole spatial transfer function}\label{sec:trans}
The dipole spatial transfer function is the spatial Fourier transform of
the dipole point spread function (or the complex autocorrelation of the dipole
coherent transfer function). Applying the Fourier transform to Eq.
\eqref{eq:paradpsf} we find that
  \begin{align}
    H(\bs{\nu}, \vartheta) \stackrel{(p)}{=} \frac{N}{\nu_c^2}\left[\text{chat}_0\left(\frac{\nu}{\nu_c}\right)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2 \text{chat}_1\left(\frac{\nu}{\nu_c}\right)\cos^2\vartheta\right].
  \end{align}
In Fig. \ref{fig:odotf} we plot the dipole spatial transfer function for
several dipole orientations and numerical apertures. We find that the dipole
spatial transfer function is negative for axial dipoles at high spatial
frequencies, especially for larger numerical apertures. The negative dipole
spatial transfer corresponds to a contrast inversion for high-frequency
patterns of axial dipoles because the irradiance minimum corresponds to the
position of the dipole.

@@

 \subsubsection{Paraxial dipole spatio-angular transfer function}
 We can calculate the dipole spatio-angular transfer function by taking the
 spatial Fourier transform of the dipole angular transfer function (or the
 spherical Fourier transform of the dipole spatial transfer function) to find
 that
 \begin{align}
H_{\ell}^m(\mb{r}) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
 \end{align}

@@

\section*{Acknowledgments}
We thank Kyle Myers, Harrison Barrett, Scott Carney, Luke Pfister, Jerome Mertz,
Mikael Backlund, Matthew Lew, Hari Shroff, Min Guo, Yicong Wu, Shalin Mehta,
Abhishek Kumar, Peter Basser, Gordon Wetzstein, Hayato Ikoma, Laura Waller, Ren
Ng, Xiaochuan Pan, Emil Sidky, Chien-Min Kao, Phillip Vargas, Dimple Modgil,
Sean Rose, Corey Smith, Scott Trinkle, and Jianhua Gong for valuable discussions
during the development of this work. TC was supported by a University of Chicago
Biological Sciences Division Graduate Fellowship, and PL was supported by a
Marine Biological Laboratory Whitman Center Fellowship.

>>>>

\author{Talon Chandler,\authormark{1,*} Hari Shroff,\authormark{2,3} Rudolf Oldenbourg,\authormark{2} and Patrick La Rivi\`ere\authormark{1,2}}

\address{\authormark{1}University of Chicago, Department of Radiology, Chicago, Illinois 60637, USA\\
  \authormark{2}Section on High Resolution Optical Imaging, National Institute
  of Biomedical Imaging and Bioengineering, National Institutes of Health,
  Bethesda, Maryland 20892, USA\\
  \authormark{3}Marine Biological Laboratory, Bell Center, Woods Hole, Massachusetts 02543, USA
}

@@

\subsubsection{Paraxial dipole spatial transfer function}\label{sec:trans}
The dipole spatial transfer function is the spatial Fourier transform of
the dipole point spread function (or the complex autocorrelation of the dipole
coherent transfer function). Applying the Fourier transform to Eq.
\eqref{eq:paradpsf} we find that
  \begin{align}
    H(\bs{\nu}, \vartheta) \stackrel{(p)}{=} \frac{N}{\nu_c^2}\left[\text{chat}_0\left(\frac{\nu}{\nu_c}\right)\sin^2\vartheta + \left(\frac{\text{NA}}{n_o}\right)^2 \text{chat}_1\left(\frac{\nu}{\nu_c}\right)\cos^2\vartheta\right].
  \end{align}
In Fig. \ref{fig:odotf} we plot the dipole spatial transfer function for
several dipole orientations and numerical apertures. We find that the dipole
spatial transfer function is negative for axial dipoles at high spatial
frequencies, especially for larger numerical apertures. The negative dipole
spatial transfer corresponds to a contrast inversion for high-frequency
patterns of axial dipoles because the irradiance minimum corresponds to the
position of the dipole.

@@

 \subsubsection{Paraxial dipole spatio-angular transfer function}
 We can calculate the dipole spatio-angular transfer function by taking the
 spatial Fourier transform of the dipole angular transfer function (or the
 spherical Fourier transform of the dipole spatial transfer function) to find
 that
 \begin{align}
H_{\ell}^m(\bv) \stackrel{(p)}{=} &\frac{N}{3\nu_c^2}\left[2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + \left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_0\delta_{\ell0}\delta_{m0}+\nonumber\\ &\frac{N}{3\nu_c^2}\left[-2\text{chat}_0\left(\frac{\nu}{\nu_c}\right) + 2\left(\frac{\text{NA}}{n_o}\right)^2\text{chat}_1\left(\frac{\nu}{\nu_c}\right)\right]\Lambda_2\delta_{\ell2}\delta_{m0}.
 \end{align}

@@

\section*{Acknowledgments}
We thank Kyle Myers, Harrison Barrett, Scott Carney, Luke Pfister, Jerome Mertz,
Sjoerd Stallinga, Mikael Backlund, Matthew Lew, Min Guo, Yicong Wu, Shalin
Mehta, Abhishek Kumar, Peter Basser, Marc Levoy, Michael Broxton, Gordon
Wetzstein, Hayato Ikoma, Laura Waller, Ren Ng, Tomomi Tani, Michael Shribak, Mai
Tran, Amitabh Verma, Xiaochuan Pan, Emil Sidky, Chien-Min Kao, Phillip Vargas,
Dimple Modgil, Sean Rose, Corey Smith, Scott Trinkle, and Jianhua Gong for
valuable discussions during the development of this work. TC was supported by a
University of Chicago Biological Sciences Division Graduate Fellowship, and PL
was supported by a Marine Biological Laboratory Whitman Center Fellowship.
